experiment 1

### 2021-11-12 experiments/experiment 1/experiment-1.Rmd
Test of experiment and change to microxanox 0.3.0 minimum version

library(microxanox)
if (packageVersion("microxanox") < package_version("0.3.0")) {
  stop("microxanox version needs to be at least 0.2.3!")
}
library(tidyverse)
library(patchwork)
library(here)
source(here("R/various_useful_functions.r"))
zero <- 0 ## don't change
unity <- 1 ## don't change!!!
options(mc.cores = 7)
eval_dynamics_flag <- FALSE
```

>>>>

library(microxanox)
if (packageVersion("microxanox") < package_version("0.3.0")) {
  stop("microxanox version needs to be at least 0.3.0!")
}
library(tidyverse)
library(patchwork)
library(here)
source(here("R/various_useful_functions.r"))
zero <- 0 ## don't change
unity <- 1 ## don't change!!!
options(mc.cores = 7)
eval_dynamics_flag <- FALSE
```
